---
title: "Manuscript Outline"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## How does the emergence of giant components affect coevolution? 

The structure of networks can range from disconnected - those composed of several isolated groups of interacting nodes - to fully connected - those composed of one single component encompassing all network nodes. 

Ecological networks are no exception (Guimarães et al. 2020; Maia et al. 202ONLY-DARWIN-KNOWS).

The phase transition between such structures is mediated by a connectivity parameter, *c*. 

Such drastic structural changes should affect how dynamics flows in these networks, for instance how species coevolve.

Here, we investigate how the emergence of connected structures on bipartite networks affects coevolution between species, specifically indirect effects and trait matching.

Example of how to add code if we want to summarise data:
```{r cars}
summary(cars)
```

Example of how to add figures by re-ploting them:
```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

Finally how to add figures which are already saved as images:
(Não consegui adicionar!)
